CGAT In The Hat

### 2012-12-07 paper/paper.tex
Adding IEEEtran.bst and modified paper.tex so that some of the ridiculous citations (Ensembl and Artemis I think) have et al instead of a list of like 50 authors.

\thispagestyle{empty}
\pagestyle{empty}

\section{Introduction}\label{sec:introduction}
Dr. Anya Goodman, a professor in the department of chemistry and biochemistry
at Cal Poly, San Luis Obispo, offers a bioinformatics course that covers
several aspects of gene annotation and genomic research. Her work is a part of
the \textit{Genomics Education Partnership} (GEP), based at Washington
University in St. Louis~\cite{gep}. GEP is an organization that aims to bring
genomics research to academic institutions, especially undergraduate classes.
This allows undergraduate students to get the opportunity to learn about, and
practice, basic genomic research and, in turn, contribute meaningful work to
the biological research community. However, GEP does not have an existing
system in which users can input and save gene annotations and get immediate
feedback regarding their performance. Similarly, available gene annotation
software--RepeatMasker, Artemis, and others~\cite{repeatmasker, artemis}--is
not designed to provide immediate feedback for users regarding their
performance. In this paper, we present Community Genome Annotation Training database,
\textit{CGAT}, a web-based gene annotation application designed to provide
feedback of gene annotation quality to students faster.

@@

This paper discusses the progress that has been made during a graduate database
class at Cal Poly, San Luis Obispo on \textit{CGAT} as well as relevant future
work. The rest of the paper is as follows. Section \ref{sec:background}
discusses the common terms and biological meanings used in the project. Section
\ref{sec:choice} explains why we chose MongoDB as our backend. Section
\ref{sec:implementation} goes into the details of how our backend and frontend
are implemented currently. Section \ref{sec:results} discusses the results of
our demo to our customer. Lastly, section \ref{sec:future} describes the future
work still left to do.

@@

When we were deciding between MongoDB and Couchbase we looked at the features they 
provided and noticed several things. First, Couchbase currently is a pure key-value store. Couchbase has
no idea what the structure of the value is. Unlike MongoDB, which can query for fields inside an 
object specified by a key. This feature of MongoDB makes updating relations (which we 
have a lot of) super easy. Second, Couchbase provides a huge
cluster/map reduce overhead that is not necessary for our data. Therefore we choose to use
MongoDB for the CGAT database.

@@

\bibliographystyle{acm}
\bibliography{refs}

>>>>

\thispagestyle{empty}
\pagestyle{empty}
\bstctlcite{test}

\section{Introduction}\label{sec:introduction}
Dr. Anya Goodman, a professor in the department of chemistry and biochemistry
at Cal Poly, San Luis Obispo, offers a bioinformatics course that covers
several aspects of gene annotation and genomic research. Her work is a part of
the \textit{Genomics Education Partnership} (GEP), based at Washington
University in St. Louis~\cite{gep}. GEP is an organization that aims to bring
genomics research to academic institutions, especially undergraduate classes.
This allows undergraduate students the opportunity to learn about, and
practice, basic genomic research and, in turn, contribute meaningful work to
the biological research community. However, GEP does not have an existing
system in which users can input and save gene annotations and get immediate
feedback regarding their performance. Similarly, available gene annotation
software--RepeatMasker, Artemis, and others~\cite{repeatmasker, artemis}--is
not designed to provide immediate feedback for users regarding their
performance. In this paper, we present Community Genome Annotation Trainer,
\textit{CGAT}, a web-based gene annotation application designed to provide
students with feedback on the quality of their gene annotations faster.

@@

This paper discusses the progress that has been made during a graduate database
class at Cal Poly, San Luis Obispo on \textit{CGAT} as well as relevant future
work. The rest of the paper is as follows. Section \ref{sec:background}
discusses the common terms and biological meanings used in the project. Section
\ref{sec:choice} explains why we chose MongoDB as our backend. Section
\ref{sec:implementation} goes into the details of how our backend and frontend
are implemented currently. Section \ref{sec:results} discusses the results of
our demo to our customer. Lastly, section \ref{sec:future} describes our future
work.

@@

When we were deciding between MongoDB and Couchbase we looked at the features they 
provided and noticed several things. First, Couchbase currently is a pure key-value store it has
no idea what the structure of the value. Unlike MongoDB, which can query for fields inside an 
object specified by a key. This feature of MongoDB makes updating relations (which we 
have a lot of) super easy. Second, Couchbase provides a huge
cluster/map reduce overhead that is not necessary for our data. Therefore we choose to use
MongoDB for the CGAT database.

@@

%\bibliographystyle{acm}
\bibliographystyle{IEEEtran}
\bibliography{refs}
